The Astropy Project

### 2017-12-11 main.tex
correct several serious issues with table formatting
remove the overly-complicated table formatting and just put it in the table specification directly

\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
the conversion from FK4 to Galactic coordinates for all pairs of tools.
This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
sub-milliarcsecond differences (light colors, small differences), while PALpy,
pySLALIB, and PyAST also agree amongst themselves.
However, there is an offset of around 0.2\arcsec\space between the two groups.
Finally, PyEphem disagrees with all other packages by 0.4--0.8\arcsec (darker
colors, large differences).
These values are only meant to be illustrative and will change over time as the
benchmarks are refined and the packages updated.

\begin{figure}
  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
  \caption{
    Comparison matrix of the accuracy values of the FK4 to Galactic
    transformation between the different packages. Each comparison block shows
    four squares representing the median, mean, maximum and standard deviation
    going from left to right and bottom to top.
    Darker colors (larger differences) are more significant disagreements.
    \label{fig:coordinate_benchmarks}
  }
\end{figure}

@@

\begin{longrotatetable}
  \begin{deluxetable*}{ccccc}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:registry}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
      \startdata
        \input{registry.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}

\begin{deluxetable*}{cccc}
  \tablecaption{Registry of provisionally accepted affiliated packages.}
  \label{tab:registry_prov}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
    \startdata
      \input{registry_prov.tex}
    \enddata
\end{deluxetable*}

>>>>

\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
the conversion from FK4 to Galactic coordinates for all pairs of tools that
implement this transformation.
In this figure, the color of the cell indicates the maximum difference (in
arcseconds) between the two tools over the 1000 longitude-latitude pairs tested.
This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
sub-milliarcsecond differences (light colors, small differences), while PALpy,
pySLALIB, and PyAST also agree amongst themselves.
However, there is an offset of around 0.2\arcsec\space between the two groups.
Finally, PyEphem disagrees with all other packages by 0.4--0.8\arcsec (darker
colors, large differences).
These values are only meant to be illustrative and will change over time as the
benchmarks are refined and the packages updated.

\begin{figure}
  \includegraphics[width=\textwidth]{coordinates-benchmark.pdf}
  \caption{
    Comparison matrix of the maximum difference between longitude-latitude
    values in a set of 1000 random points transformed from FK4 to Galactic
    with the different packages.
    Darker colors (larger differences) are more significant disagreements.
    \label{fig:coordinate_benchmarks}
  }
\end{figure}

@@

\begin{longrotatetable}
    \begin{deluxetable*}{cccp{3in}c}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:registry}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
      \startdata
        \input{registry.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}

\begin{deluxetable*}{cccp{3in}c}
  \tablecaption{Registry of provisionally accepted affiliated packages.}
  \label{tab:registry_prov}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
    \startdata
      \input{registry_prov.tex}
    \enddata
\end{deluxetable*}
